---
title: "Untitled"
output: github_document
---

##Read sample genotypes data from ENSEMBLE

We downloaded genotype data from ENSEMBLE on the MXL Mexican Ancestry in Los Angeles, California dataset

What proportion of this data are G/G etc?

```{r}
mxl <- read.csv("373531-SampleGenotypes-Homo_sapiens_Variation_Sample_rs8067378.csv")

mxl
```

We want to look at the second column that contains the genotype information

```{r}
table(mxl$Genotype..forward.strand.)
```

##RNA-Seq result analysis for different genotypes of this SNP

```{r}
expr <- read.table("rs8067378_ENSG00000172057.6.txt")
head(expr)
```

```{r}
plot(expr$geno, col="pink")
```

```{r}
summary(expr[ expr$geno == "G/G",]$exp)

```


```{r}
hist(expr[expr$geno == "G/G",]$exp, breaks=20)
```


```{r}
summary(expr[ expr$geno == "A/G",]$exp)

```

```{r}
hist(expr[expr$geno == "A/G",]$exp, breaks=20)

```


```{r}
summary(expr[ expr$geno == "A/A",]$exp)

```

```{r}
hist(expr[expr$geno == "A/A",]$exp, breaks=20)

```

##Try a boxplot

We will use the `boxplot()` function and the input data will be **expr**. How do we draw a useful plot?

```{r}
boxplot(exp ~ geno, data=expr, notch=T)
```


How many samples are we looking at here?
```{r}
nrow(expr)
```














