---
title: "class 10"
author: "Sunyoung Lee"
date: "February 7, 2020"
output:github_document
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Get our input data

Our data for today come from the Wisconsin Breast Cancer Diagnostic Data Set

```{r}
wisc.df <- read.csv("WisconsinCancer.csv")
head(wisc.df)
```

```{r}
wisc.data <- as.matrix(wisc.df[,3:32])
head(wisc.data)
```

> Q. how many patients are there in this dataset?

```{r}
nrow(wisc.df)
```


> Q. How many cancer and non-cancer patients are there?

```{r}
table(wisc.df$diagnosis)
```

```{r}
sum(wisc.df$diagnosis == "M")
```

> Q. How many cols are "_mean" values?

```{r}
colnames(wisc.df)
```

We can use the "grep()" function to see this

```{r}
grep("_mean", colnames(wisc.df), value = TRUE)
```

We can take the `length()` of this to find how many mathces there are
```{r}
length(grep("_mean", colnames(wisc.df)))
```

## Enter Principal Component Analysis 

First we need to check whether our input data should be scaled. Let's check the sd() and mean() of all our colums in `wisc.data`

```{r}
round( apply(wisc.data, 2, sd), 2)
```

## Perform PCA on wisc.data by completing the following code
```{r}
wisc.pr <- prcomp(wisc.data, scale=TRUE)
summary(wisc.pr)
```

```{r}
biplot(wisc.pr)
```

This is a hot mess! We need to cook our own PCA plot. To do this we need to access the results within the `wisk.pr` object.

```{r}
attributes(wisc.pr)
```

We want the$x component to make our PCA plot

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=wisc.df$diagnosis)
```

```{r}
#install.packages("factoextra")
```

```{r}
library(factoextra)
fviz_eig(wisc.pr, addlabels = TRUE)
```

```{r}
plot(pve, xlab = "Principal Component", 
     ylab = "Proportion of Variance Explained", 
     ylim = c(0, 1), type = "o")
```

```{r}
data.scaled <- scale(wisc.data)
```

###Hierarchical clustering
Can we find a separation of cancer from non-cancer using a clustering method on the original input data

```{r}
library(factoextra)
fviz_eig(wisc.pr, addlabels = TRUE)
```

```{r}
barplot(pve, ylab = "Precent of Variance Explained",
     names.arg=paste0("PC",1:length(pve)), las=2, axes = FALSE)
axis(2, at=pve, labels=round(pve,2)*100 )
```

```{r}
wisc.pr.hc <- hclust( dist(wisc.pr$x[,1:3]), method="ward.D2")
plot(wisc.pr.hc)
```

```{r}
grps <- cutree(wisc.pr.hc, k=2)
table(grps)
```

```{r}
table(grps, wisc.df$diagnosis)
```

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=grps)
```

```{r}
url <- "https://tinyurl.com/new-samples-CSV"
new <- read.csv(url)
npc <- predict(wisc.pr, newdata=new)
npc
```

```{r}
plot(wisc.pr$x[,1], wisc.pr$x[,2], col=wisc.df$diagnosis)
points(npc[,1], npc[,2], col="blue", pch=16, cex=3)
text(npc[,1], npc[,2], labels=c(1,2), col="white")
```

