---
title: "lecture 09"
author: "Sunyoung Lee"
date: "February 5, 2020"
output: github_document
---
## K-means clustering

Let's try the "kmeans()" function in R to cluster som emade-up example data

```{r}
tmp <- c(rnorm(30,-3), rnorm(30,3))
x <- cbind(x=tmp, y=rev(tmp))

plot(x)
```
Use the kmeans() function setting k to 2 and nstart = 20
```{r}
km  <- kmeans (x, centers = 2, nstart = 20)
```
```{r}
km
```


what is in the output object `km` I can use the `attributes()` function to find this info
```{r}
attributes(km)
```
Q. How many points are in each cluster?
```{r}
km$size
```

Q. what 'component' of your result object details
  - cluster size?
  - cluster assignment/membership?
  - cluster center?

```{r}
km$cluster
```

let's check how many 2s and 1s are in this vector with the "table()" function.
```{r}
table(km$cluster)
```

Plot x colored by the kmeans cluster assignment and add cluster centers as blue points

```{r}
plot(x, col=km$cluster+321)
points(km$centers, col="blue", pch=1, cex=3)
```












## Hierarchical clustering in R

The `hclust()` function is the main Hierarchical clustering method in R and it **must** be passed a **distance matrix** as input not your raw data!

```{r}
hc <- hclust( dist(x) )
hc
```

```{r}
plot(hc)
abline(h=6, col="pink", lty=2)
abline(h=4, col="light blue", lty=2)

```

```{r}
cutree(hc, h=6)
```

```{r}
table(cutree(hc, h=3.5))
```

You can also ask `cutree()` for the `k` number of groups that you want.
```{r}
cutree(hc, k=5)
```

```{r}
x <- rbind(
 matrix(rnorm(100, mean=0, sd=0.3), ncol = 2), # c1
 matrix(rnorm(100, mean=1, sd=0.3), ncol = 2), # c2
 matrix(c(rnorm(50, mean=1, sd=0.3), # c3
 rnorm(50, mean=0, sd=0.3)), ncol = 2))
colnames(x) <- c("x", "y")
```

```{r}
plot(x)
col <- as.factor( rep(c("c1","c2","c3"), each=50) )
plot(x, col=col)

```

Q. Use the dist(), hclust(), plot() and cutree()
 functions to return 2 and 3 clusters
 
Q. How does this compare to your known 'col' groups?


```{r}
hc <- hclust(dist(x))
plot(hc)

```

```{r}
grps3 <- cutree(hc, k=3)
grps3
```

```{r}
table(grps3)
```

```{r}
plot(x,col=grps3)
```

```{r}
table(grps3, col)
```

#principal component analysis (PCA)

The main function in base R for PCA is called `prcomp()`. Here we will use PCA to examine the funny food that folks eat in the UK and N. Ireland.

```{r}
x <- read.csv("UK_foods.csv", row.names = 1)
x
```
Make some conventional plots
```{r}
pairs(x, col=rainbow(10), pch=16)
```

#PCA to the rescue
```{r}
pca <- prcomp( t(x) )
```

```{r}
summary(pca)
```
```{r}
attributes(pca)
```

```{r}
pca
```

```{r}
plot(pca$x[,1], pca$x[,2])
text(pca$x[,1], pca$x[,2], labels = colnames(x), col=c("black","red","blue","dark blue"))
```

```{r}
plot(pca)
```

