---
title: "Untitled"
output: github_document
---

## Coronavirus

Here we analyze infection data for the 2019 novel Coronavirus COVID-19 (2019-nCoV) epidemic. The raw data is pulled from the Johns Hopkins University Center for Systems Science and Engineering (JHU CCSE) Coronavirus repository.


```{r}
url <- "https://tinyurl.com/COVID-2019"
virus <- read.csv(url)

tail(virus)
```


> Q1. How many total infected cases are there around the world?

```{r}
total_cases <- sum(virus$cases)
total_cases
```

Lets have a look at the *$type* column

```{r}
table(virus$type)
```

> Q2. How many deaths linked to infected cases have there been?

```{r}
inds <- virus$type == "death"
death_cases <- sum(virus[inds,"cases"])
death_cases
```

> Q3. What is the overall death rate?

```{r}
round(death_cases/total_cases * 100, 2)
```

> Q4. What is the death rate in "Mainland China"?

```{r}


library(tidyverse)
mainland_china <- virus%>%
  filter(Country.Region == "Mainland China")

death_rate_mc <- mainland_china%>%
  group_by(type)%>%
  summarize_if(is.numeric, sum)%>%
  ungroup()%>%
  mutate(rate = cases/sum(cases)*100)

death_rate_mc%>%
  filter(type == "death")%>%
  select(rate)

```

> Q5. What is the death rate in Italy, Iran and the US?

```{r}
library(DescTools)
death_rate_all <- virus%>%
  group_by(type, Country.Region)%>%
  summarize_if(is.numeric, sum)%>%
  ungroup()%>%
  group_by(Country.Region)%>%
  mutate(rate = cases/sum(cases)*100)

death_rate_all%>%
  filter(Country.Region %like any% c("Italy", "Iran", "US"),
         type == "death")%>%
  select(Country.Region, rate)

```





