---
title: 'class 6: R functions'
author: "Sunyoung Lee"
date: "January 24, 2020"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## This is a level 2 heading

This is a **regular** old *text*!

and a list of stuff



- thing one
- ting two
- and another thing


```{r}
plot(1:5, col="blue", type="o")
```

let's insert a code chunk with the shortcut `Option-CMD-i`:

```{r}
x <- c(1:10)
x
```

Here is my analysis of your new data. It looks ok.. the mean of your data is `r mean(x)`.

## More on reading input files

We will use the read.table() function again.

```{r}
read.table("test1.txt")
```
```{r}
x <- read.table("test1.txt", header = TRUE, sep=",")
```

```{r}
read.csv("test1.txt")
```

Try the 2nd file

```{r}
read.table("test2.txt", sep="$", header=T)
```

```{r}
read.table("test3.txt")
```

## Our first function

This is an example function named `add` with input `x` and `y`

```{r}
add <- function(x, y=1) {
 # Sum the input x and y
 x + y
}
```

Lets try using it

^
```{r}
add(x=c(1,6,2),y=4)
```

```{r}
add(1,6)
```







```{r}
x <- c(10,4,22,6)
min(x)
max(x)
#range(x)
```

A 2nd example function to re-scale data to lie between 0 and 1

```{r}
rescale <- function(x) {
 rng <-range(x)
 (x - rng[1]) / (rng[2] - rng[1])
}
```

Lets test this function

```{r}
rescale(c(1:10, 30, 100))
```

```{r}
rescale( c(1:10, NA))
```

```{r}
x <- c(1:10, NA)
rng <- range(x, na.rm=T)
rng
```
```{r}
?range
```

```{r}
rescale2 <- function(x) {
  rng <- range(x, na.rm=TRUE)
  (x - rng[1]) / (rng[2]-rng[1])
}

```


```{r}
rescale2( c(1:10, NA) )
```

Taking things a bit too far...

```{r}
rescale3 <- function(x, na.rm=TRUE, plot=FALSE) {
 if(na.rm) {
 rng <-range(x, na.rm=na.rm)
 } else {
 rng <-range(x)
 }
 print("Hello")
 
 answer <- (x - rng[1]) / (rng[2] - rng[1])

 
 print("is it me you are looking for?")
 if(plot) {
print("please don't sing again!")
 plot(answer, typ="b", lwd=4)
 }
 print("I can see it in ...")
}
```

```{r}
rescale3(x, plot=TRUE)
```



## Working with the bio3d package

To use the functions from any packagewe have installed we use the `library()` function to load it. 

```{r}
library(bio3d)
```


```{r}
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s3, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

```{r}
hc <- hclust( dist( rbind(s1.b, s2.b, s3.b) ) )
plot(hc)
```


```{r}
s1 <- read.pdb("4AKE")
s1
```
```{r}
class(s1)
```

```{r}
str(s1)
```


```{r}
s1$seqres
```

```{r}
s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s1.chainA
```

```{r}
?trim.pdb
```


```{r}
plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
points(s2.b, col="light blue", typ="l", lwd =3)
points(s3.b, col="pink", typ="l", lwd = 3)
```

```{r}
library(bio3d)
s1 <- read.pdb("4AKE") # kinase with drug
s2 <- read.pdb("1AKE") # kinase no drug
s3 <- read.pdb("1E4Y") # kinase with drug

s1.chainA <- trim.pdb(s1, chain="A", elety="CA")
s2.chainA <- trim.pdb(s2, chain="A", elety="CA")
s3.chainA <- trim.pdb(s1, chain="A", elety="CA")

s1.b <- s1.chainA$atom$b
s2.b <- s2.chainA$atom$b
s3.b <- s3.chainA$atom$b

plotb3(s1.b, sse=s1.chainA, typ="l", ylab="Bfactor")
plotb3(s2.b, sse=s2.chainA, typ="l", ylab="Bfactor")
plotb3(s3.b, sse=s3.chainA, typ="l", ylab="Bfactor")
```

